Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/inverted_u.tex
Revised top para.

\begin{finding}
\textit{For sufficiently low warm start under the instances that are relative reputation costly, the unique pure Nash equilibrium strategies in the competition game are:\footnote{the uniqueness comes from the fact that we break indifferences towards easier to deploy algorithms}
\begin{center}
\textbf{Permanent Monopoly} - $\DG$ \\
\textbf{Temporary Monopoly} (incumbent)- $\TS$ \\
\textbf{Permanent Duopoly} - $\DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}

@@

For the relative reputation costly instances,\footnote{We defer the table for uniform instances to the appendix. Summarizing the results, we see that, for low warm start, \DG yields more than half the market against \TS but is indifferent between \DG and \DEG. Since we break indifference towards easier to deploy algorithms, we also find that \DG is the incentivized algorithm in equilibrium} we see that, for low warm start, $\DG$ is a weakly dominant strategy for the competition game, and in particular weakly dominates $\TS$. This establishes our claim that $\DG$ is the incentivized algorithm.

The reason we see that $\DG$ weakly dominates under the Heavy Tail and Uniform instances but that $\TS$ is weakly dominant under Needle In Haystack is precisely due to the fact that the purposeful exploration engaged by $\TS$ in the early rounds leads it to suffer a relative reputational cost in the former case but not in the latter. Looking at the relative reputation plots in Figure \ref{relative_rep_plots}, we can interpret fixing a warm start $T_0$ as fixing the starting point on the relative reputation plots. The proportion of first rounds in the competition game that will go to a firm playing alg $A$ over a firm playing alg $B$ will correspond to the relative reputation proportion at time $T_0$. As a result, we see that for warm start $T_0 = 20$ on the relative reputation costly instances, $\DG$ will win the first agent in a larger proportion of the simulations than $\TS$. However, on the Needle In Haystack instances, we see that $\TS$ wins a larger proportion of the first agents compared to $\DG$.

@@

\xhdr{Temporary Monopoly.} Recall that the incumbent firm enters the
market and serves as a monopolist until the entrant firm enters at
round $X$. \gaedit{For this section we focus on the warm start values and on the relative reputation costly instances where we observed that, under permanent duopoly, $\DG$ was the weakly dominant strategy. Concretely, our presented results are for $T_0 = 20$.} \footnote{However, we report the results for the Needle In Haystack instances in the supplementary
  material. The results are unsurprising, where $\TS$ is the dominant
  strategy for both the entrant and incumbent.}

>>>>

\ascomment{stopped here.}

\begin{finding}
\textit{For sufficiently low warm start under the instances that are exploration-disadvantaged, the unique pure Nash equilibrium strategies in the competition game are:\footnote{the uniqueness comes from the fact that we break indifferences towards easier to deploy algorithms}
\begin{center}
\textbf{Permanent Monopoly} - $\DG$ \\
\textbf{Temporary Monopoly} (incumbent)- $\TS$ \\
\textbf{Permanent Duopoly} - $\DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}

@@

For the exploration-disadvantaged instances,\footnote{We defer the table for uniform instances to the appendix. Summarizing the results, we see that, for low warm start, \DG yields more than half the market against \TS but is indifferent between \DG and \DEG. Since we break indifference towards easier to deploy algorithms, we also find that \DG is the incentivized algorithm in equilibrium} we see that, for low warm start, $\DG$ is a weakly dominant strategy for the competition game, and in particular weakly dominates $\TS$. This establishes our claim that $\DG$ is the incentivized algorithm.

The reason we see that $\DG$ weakly dominates under the Heavy Tail and Uniform instances but that $\TS$ is weakly dominant under Needle In Haystack is precisely due to the fact that the purposeful exploration engaged by $\TS$ in the early rounds leads it to suffer a relative reputational cost in the former case but not in the latter. Looking at the relative reputation plots in Figure \ref{relative_rep_plots}, we can interpret fixing a warm start $T_0$ as fixing the starting point on the relative reputation plots. The proportion of first rounds in the competition game that will go to a firm playing alg $A$ over a firm playing alg $B$ will correspond to the relative reputation proportion at time $T_0$. As a result, we see that for warm start $T_0 = 20$ on the exploration-disadvantaged instances, $\DG$ will win the first agent in a larger proportion of the simulations than $\TS$. However, on the Needle In Haystack instances, we see that $\TS$ wins a larger proportion of the first agents compared to $\DG$.

@@

\xhdr{Temporary Monopoly.} Recall that the incumbent firm enters the
market and serves as a monopolist until the entrant firm enters at
round $X$. \gaedit{For this section we focus on the warm start values and on the exploration-disadvantaged instances where we observed that, under permanent duopoly, $\DG$ was the weakly dominant strategy. Concretely, our presented results are for $T_0 = 20$.} \footnote{However, we report the results for the Needle In Haystack instances in the supplementary
  material. The results are unsurprising, where $\TS$ is the dominant
  strategy for both the entrant and incumbent.}
